Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-11-20 manuscript/paper-tycho.tex
Add profile fits, fix spec.var.model, radio prfs
Entire profile fitting for both radio/X-ray data
Critical (output affecting) bug fix to modeling spectral variation
Ad hoc code to extract/parse/plot radio profiles
Split model parameter space plots to new notebook

% ========
% Appendix
% ========
%\clearpage
\appendix

@@

\begin{figure*}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/energywidth-subplot-sn1006.pdf}
    \caption{Rim width predictions for loss-limited and damped fits with
    $\mu = 1$ fixed for all regions, SN 1006.}
\end{figure*}

% Fit results for ALL regions, mu = 1, loss-limited and damped
\begin{table}[h]
    \footnotesize
    \centering
    \caption{Best model fits for all regions, $\mu = 1$}
    \input{suppl-fits-all-sn1006.tex}
    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
        best damped fits select best $a_b$ value below $0.01$ (to $0.002$),
        enforcing moderate damping.  All fits have 1 dof.  The manual selection
        of a best $a_b$ value may be construed as removing one more dof.}
\end{table}

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.48\textwidth]{figures/mE-damp-sn1006.pdf}
    }{
        \includegraphics[width=0.35\textwidth]{figures/mE-damp-sn1006.pdf}
    }
    \caption{Curves of $\mE$ values for best damping fits for all regions,
        SN 1006}
\end{figure}

>>>>

% ========
% Appendix
% ========
\clearpage
\appendix

@@

\begin{figure*}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/energywidth-subplot-sn1006.pdf}
    \caption{Rim width predictions for loss-limited (dashed) and damped fits
        (solid) with $\mu = 1$ fixed for all regions, SN 1006.}
\end{figure*}

% Fit results for ALL regions, mu = 1, loss-limited and damped
\begin{table}[h]
    \footnotesize
    \centering
    \caption{Best model fits for all regions, $\mu = 1$}
    \input{suppl-fits-all-sn1006.tex}
    \tablecomments{Loss-limited fits have $\mu=1$ fixed;
        best damped fits select best $a_b$ value between $0.002$ and $0.01$
        (1.8--9 arcsec; $a_b$ is given in units of shock radius $r_s$),
        enforcing moderate damping.  All fits have 1 dof.  The manual selection
        of a best $a_b$ value may be construed as removing one more dof.}
\end{table}

\clearpage
\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.48\textwidth]{figures/mE-damp-sn1006.pdf}
    }{
        \includegraphics[width=0.35\textwidth]{figures/mE-damp-sn1006.pdf}
    }
    \caption{Curves of $\mE$ values for best damping fits for all regions,
        SN 1006}
\end{figure}
